Target Markdown

### 2023-04-14 _targets.Rmd
...

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "plyr"
                            ))

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt"
                            ))
